---
title: "Health Impact of Tornado App"
author: "Koji"
date: "2018/7/22"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(dplyr)
library(knitr)
library(leaflet)
```

# Course project

This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

```{r, cache=TRUE}
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2", destfile = "repdata-data-StormData.csv.bz2")
stormData <- read.csv("repdata-data-StormData.csv.bz2", header = TRUE, stringsAsFactors = FALSE)
extractData <- stormData %>%
        filter(as.POSIXct(stormData$BGN_DATE, format = "%m/%d/%Y %H:%M:%S") > "2010-12-31") %>%
        select(BGN_DATE, EVTYPE, FATALITIES, INJURIES, LATITUDE, LONGITUDE)
```

## Our App Address | the question:

- Across the United States, which types of events are most harmful with respect to population health thru the century?

### Links

- [Health Impact Of Tornado App](https://dr-orange-jr.shinyapps.io/HealthImpactOfTornadoApp/)
- [GitHub repo](https://github.com/dr-orange/Developing-Data-Products/tree/master/ShinyApplicationAndReproduciblePitch)

## The tornado is the most harmful

```{r echo=FALSE}
humanImpactTop10 <- extractData %>%
        # fatalities and injuries
        mutate(PERSONS = FATALITIES + INJURIES) %>%
        select(EVTYPE, PERSONS) %>%
        # summarize each event type
        group_by(EVTYPE) %>%
        summarize_all(sum) %>%
        # top 10
        top_n(10, PERSONS)

ggplot(data = humanImpactTop10, aes(x = reorder(EVTYPE, -PERSONS), y = PERSONS)) +
        geom_bar(stat = "identity", position = position_dodge(), fill = "orangered") +
        theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
        labs(x = "Weather event", y = "Total health impact [persons]") +
        ggtitle("Top 10 Harmful Events")
```


## How much tornado hurt to what region

```{r}
tornado <- extractData %>%
        filter(EVTYPE == "TORNADO") %>%
        # fatalities and injuries
        mutate(PERSONS = FATALITIES + INJURIES, 
               LATITUDE = LATITUDE / 100, 
               LONGITUDE = - LONGITUDE / 100) %>%
        filter(PERSONS > 10) %>%
        select(PERSONS, LATITUDE, LONGITUDE)

leaflet(tornado) %>%
        addTiles() %>%
        addCircles(
                lng = ~LONGITUDE, lat = ~LATITUDE, weight = 1,
                radius = ~sqrt(PERSONS) * 5000
        )
```
