---
title: "R Markdown Presentation & Plotly"
author: "Koji"
date: "2018/7/21"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(plotly)
library(dplyr)
library(knitr)
# Load data
data(mtcars)
```

# Course project

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!


## Motor Trend

We are particularly interested in the following two questions:

- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

## Calculate correlation

`wt`, `disp` and `cyl` show high correlation.

```{r cars, echo = TRUE}
kable( cor( mtcars[, c(1, 9, 6, 3, 2)]), digits = 2)
```

## Summary {.smaller}

```{r, message=FALSE, echo=TRUE}
betterFit <- lm(mpg ~ am + wt + disp + cyl, mtcars)
summary(betterFit)
```

## Residuals vs Leverage

```{r, message=FALSE}
plot <- ggplot(betterFit, aes(.hat, .stdresid)) +
        geom_point(aes(size = .cooksd, color = .cooksd)) +
        scale_color_continuous(low = "darkgrey", high = "orangered") +
        ylab("Standardized Residuals (.stdresid)") +
        xlab("Leverage (.hat)") +
        geom_smooth(se = FALSE)
ggplotly(plot)
```

# Thank you!
